\documentclass[12pt, a4paper]{article}
\setcounter{secnumdepth}{4}


% A pretty common set of packages
\usepackage{physics}
\usepackage{algorithm2e}
\usepackage{braket}
\usepackage{mathtools}
\usepackage[margin=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{engord}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[skip=2pt,font=footnotesize,justification=centering]{caption}
\usepackage[colorlinks=true,
    linkcolor=black,          % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=black]{hyperref}
\usepackage{amstex}


\renewcommand\bibname{References}
\graphicspath{ {./figures/} }

% Do you prefer Sans Serif fonts?
%\usepackage{sfmath}
%\renewcommand{\familydefault}{\sfdefault} 


% Make some additional useful commands
\newcommand{\ie}{\emph{i.e.}\ }
\newcommand{\eg}{\emph{e.g.}\ }
\newcommand{\etal}{\emph{et al}}
\newcommand{\sub}[1]{$_{\textrm{#1}}$}
\newcommand{\super}[1]{$^{\textrm{#1}}$}
\newcommand{\degC}{$^{\circ}$C}
\newcommand{\wig}{$\sim$}
\newcommand{\ord}[1]{\engordnumber{#1}}
\newcommand{\num}[2]{$#1\,$#2}
\newcommand{\range}[3]{$#1$-$#2\,$#3}
\newcommand{\roughly}[2]{$\sim\!#1\,$#2}
\newcommand{\area}[3]{$#1 \! \times \! #2\,$#3}
\newcommand{\vol}[4]{$#1 \! \times \! #2 \! \times \! #3\,$#4}
\newcommand{\cube}[1]{$#1 \! \times \! #1 \! \times \! #1$}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\eqnref}[1]{Equation~\ref{#1}}
\newcommand{\tableref}[1]{Table~\ref{#1}}
\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\XC}{\emph{exchange-correlation}}
\newcommand{\abinit}{\emph{ab initio}}
\newcommand{\Abinit}{\emph{Ab initio}}
\newcommand{\Lonetwo}{L1$_{2}$}
\newcommand{\Dznt}{D0$_{19}$}
\newcommand{\Dtf}{D8$_{5}$}
\newcommand{\Btwo}{B$_{2}$}
\newcommand{\fcc}{\emph{fcc}}
\newcommand{\hcp}{\emph{hcp}}
\newcommand{\bcc}{\emph{bcc}}
\newcommand{\Ang}{{\AA}}
\newcommand{\inverseAng}{{\AA}$^{-1}$}
%\newcommand{\comment}[1]{}
\newcommand{\comment}[1]{\textcolor{red}{[COMMENT: #1]}}
\newcommand{\more}{\textcolor{red}{[MORE]}}
\newcommand{\red}[1]{\textcolor{red}{#1}}


% Change this to modify look of header and footer
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\thepage{}}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

    \onehalfspacing

    {\centering
    {\LARGE Analysis of NP and QMA Problems Energy Landscape Using Mutually Unbiased Bases \par}
    {\Medium M.Sc. Research Proposal }

    {\Small Hadar Tojarieh \par }
    {\Small Advisor: Assoc. Prof. Tal Mor \par }
    {\Small Technion - Israel Institute of Technology\\}
    \today
    \par
    }

    \singlespacing

    \begin{abstract}
        In quantum mechanics, Mutually Unbiased Bases (MUB) are sets of quantum states that are maximally distinct
        from one another and exhibit a lack of information when a state from one basis is measured in another basis.
        These MUB represent a powerful tool for characterizing quantum states.
        Our primary objective is to demonstrate the utility of MUB in obtaining a reliable energy landscape
        for optimization problems.
        The energy landscape, as a tool for optimization, potentially plays a crucial role in efficiently identifying
        the global minimum solution while avoiding local minima and barren plateaus when dealing with problems (or cases) that are not NP-hard.
        Our secondary goal, regards the field of not NP-hard problems,
        is integrating the MUB approach with machine learning techniques to enhance the efficiency of the
        optimization process.
        This integration aims to reduce the number of search steps required to reach the optimal
        solution and represents a novel approach to the optimization of NP problems and QMA problems which can be modeled as
        quantum systems.
    \end{abstract}

    \tableofcontents

    \onehalfspacing


    \section{Introduction and Background}\label{sec:introduction-and-background}
    \input{introduction-and-background}

    \section{Related Work}\label{sec:related-work}
    There are few parers about using quantum annealing to solve those kind of optimization problems, that are intractable
    for classical computers.
    Quantum Annealing (QA) is a method for solving optimization problems that is inspired by the process of annealing in
    metallurgy.
    Like classical simulated annealing, it is a method that uses a random search to find the global minimum
    of an energy function, but it uses the principles of quantum mechanics to guide the search.
    In QA, the optimization problem is mapped to a physical system, called the quantum annealer,
    which consists of a large number of interacting quantum bits (qubits).
    The energy function of the optimization problem is encoded into the Hamiltonian of the quantum annealer,
    and the ground state of the Hamiltonian corresponds to the optimal solution of the problem.

    The quantum annealer is initialized in a high-energy state,
    and then it is slowly cooled down to its ground state by applying a time-dependent Hamiltonian.
    The cooling process is guided by a schedule that controls the rate of change of the Hamiltonian.
    The schedule is designed to avoid getting stuck in local minima and to increase the chances of finding the global minimum.


    \section{Objectives of the Research}\label{sec:objectives-of-the-research}
    The purpose of the M.Sc. research is to configure a way to draw the energy landscape of a quantum system using MUB.
    Through that, a great number of realizations can be reached, for example avoid local minima and find the absolute minimum, avoid barren plateaus\@.
    In our research, we are going to focus on a problem which preoccupies the entire optimization world, the Vehicle Routing Problem.
    Although our research will focus on this problem as our quantum system, one can refer to other NP-hard problem, after the usage of MUB as
    a potential tool for drawing the energy landscape will be demonstrated.
    In the pursuit of our research objective, the utilization of quantum algorithmss and the implementation of a hybrid
    quantum-classical approach may provide significant benefits.
    In particular, the modeling of our problem into
    VQE or QAOA has the potential to offer
    improved approximations and the discovery of larger subclasses of NP-hard problems that are not NP-hard themselves.\\
    Despite the limitations imposed by shallow quantum circuits, such a hybrid solution may still outperform traditional
    classical methods, providing a promising avenue for further exploration and advancement in the field.
    VRP can be modeled as a search for the global minimum of an energy function, when the energy function represents
    the cost of a particular solution, such as the total distance traveled by vehicles or the total time taken to visit
    all customers.
    The configuration space is defined by the possible routes and the assignments of customers to vehicles.
    The global minimum of the energy function corresponds to the optimal solution of the problem\@.\\
    The search in the energy space can be done by using machine learning model or neural networks, for the correct differential
    fluctuations needed in the angles of each quantum eigenstate of the mutually unbiased bases in use.
    The use of machine learning in the context of MUB is motivated by two main considerations.
    Firstly, the exponential growth of the number of MUB states for a large number of qubits necessitates the development
    of techniques for efficiently selecting a portion of these states or selecting them only for a subset of qubits.
    Secondly, even for small numbers of qubits, there is a need for innovative methods to explore the space beyond the
    vicinity of MUB states.
    This approach can significantly reduce the computational resources required for the VQE algorithm,
    making it more scalable for larger problems.
    We think about using MUB to construct energy landscapes of quantum systems using machine learning techniques.
    This can provide new insights into the behavior of the system that can be hard to gain by using other methods.
    The application of machine learning algorithms can help to overcome challenges by allowing for the
    characterization of smaller-scale problems and facilitating the transfer of insights to more complex systems with a
    larger number of qubits.
    In order to gain a comprehensive understanding of the landscape, it is necessary to not only examine the exact
    MUB-states points but also their surrounding regions.
    This can be achieved through two methods:
    By initiating the quantum circuit at each MUB state while incorporating a parametrized circuit that combines the MUB state
    with a standard ansatz.
    By starting at each MUB state and constructing a small-angle ansatz through the implementation of small-angle
    rotations of each qubit and small-angle rotations of the controlled-phase operation.


    \section{Other Research Directions}\label{sec:other-research-directions}
    In addition to our main research topic, Prof. Mor and I are collaborating on other research problems.
    We plan to expand Qandies \cite{lin2020quantum} \cite{lin2021quantum} \cite{mor2022digital} terminology
    usage for explaining other quantum key distribution protocols and quantum phenomenas such as
    entanglement-swapping and delay-choice entanglement-swapping~\cite{ma2016delayed}.

    \bibliography{bibi}
    \bibliographystyle{unsrt}
\end{document}